Structured Versus Decorated Cospans

### 2020-11-25 cospans.tex
small fixes

\begin{lem}[Hermida] \label{lem:fibrewiselimits}
Suppose $\J$ is a small category and $U\maps\X\to\A$ is an opfibration. If the base $\A$ has $\J$-colimits,
the following are equivalent:
\begin{enumerate}
 \item all fibres have $\J$-colimits, and the reindexing functors preserve them;
 \item the total category $\X$ has $\J$-colimits, and $U$ (strictly) preserves them.
\end{enumerate}
\end{lem}

@@

\begin{lem}[Gray] \label{prop:opfibtolari}
  Let $U \maps\X \to \A$ be an opfibration. Then
  $U$ is a right adjoint `left inverse', a.k.a the unit is the identity, if (and only if) its fibers have
  initial objects which are preserved by the
  reindexing functors.
\end{lem}

@@

\begin{proof}  
This is due to Grothendieck; a proof can be found, for example, in \cite[\S~1.10]{Jacobs}.
\end{proof}

>>>>

\begin{lem}[\textbf{Hermida}] \label{lem:fibrewiselimits}
Suppose $\J$ is a small category and $U\maps\X\to\A$ is an opfibration. If the base $\A$ has $\J$-colimits,
the following are equivalent:
\begin{enumerate}
 \item all fibres have $\J$-colimits, and the reindexing functors preserve them;
 \item the total category $\X$ has $\J$-colimits, and $U$ (strictly) preserves them.
\end{enumerate}
\end{lem}

@@

\begin{lem}[\textbf{Gray}] \label{prop:opfibtolari}
  Let $U \maps\X \to \A$ be an opfibration. Then
  $U$ is a right adjoint `left inverse', a.k.a the unit is the identity, if (and only if) its fibers have
  initial objects which are preserved by the
  reindexing functors.
\end{lem}

@@

\begin{proof}  
The idea goes back to Grothendieck; a proof can be found in, for example, \cite[Section 1.10]{Jacobs}.
\end{proof}
